\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc}

% Toggle font: set to true for Inter, false for Latin Modern (default)
\newif\ifuseinter\useinterfalse  % <-- change to \useintertrue for Inter font
\ifuseinter\usepackage{inter}\fi
\usepackage[export]{adjustbox}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage[scale=0.90]{geometry}

% moderncv configuration
\moderncvstyle{classic}
\moderncvcolor{black}

% Add spacing above and below subsection headings globally
\let\origsubsection\subsection
\renewcommand{\subsection}[1]{\vspace{1em}\origsubsection{#1}\vspace{0.5em}}

% Author role symbols for publication lists
\newcommand{\phd}{\textcolor{red}{\textsuperscript{$\blacksquare$}}}
\newcommand{\ug}{\textcolor{blue}{\textsuperscript{$\blacksquare$}}}
\newcommand{\pg}{\textcolor{green}{\textsuperscript{$\blacksquare$}}}
\newcommand{\postdoc}{\textcolor{magenta}{\textsuperscript{$\bullet$}}}

\definecolor{confblue}{HTML}{0B2E83}
\definecolor{accent}{HTML}{1A5276}
\definecolor{highlight}{HTML}{922B21}

% Clickable title if URL is provided; otherwise prints plain title
\newcommand{\ptitle}[2]{%
  \IfStrEq{#1}{}{#2}{\href{#1}{#2}}%
}

% Conference short name in dark blue (bold)
\newcommand{\conf}[1]{\textcolor{accent}{\textbf{#1}}}

\firstname{Ambuj}
\familyname{Varshney}
\title{Curriculum Vitae}

\begin{document}

\section{Personal Information}
\cvitem{Name}{Ambuj Varshney}
\cvitem{Nationality}{Sweden}
\cvitem{Date of Birth}{October 9, 1986}
\cvitem{Mobile}{+46 72 033 85 74}
\cvitem{Email}{ambujvarshney@acm.org}

\section{Overview}
\cvitem{}{I founded the WEISER group at the National University of Singapore.}
\cvitem{}{\begin{itemize}[leftmargin=*, itemsep=4pt, parsep=0pt, topsep=0pt]
\item \textcolor{accent}{\textbf{Mentorship:}} Currently advise \textbf{\textcolor{highlight}{six}} PhD students and \textbf{\textcolor{highlight}{three}} master's students. Graduated \textbf{\textcolor{highlight}{one}} PhD student, \textbf{\textcolor{highlight}{two}} postdoctoral researchers, \textbf{\textcolor{highlight}{sixteen}} master's students, and supervised over \textbf{\textcolor{highlight}{twenty}} undergraduate students.
\item \textcolor{accent}{\textbf{Funding:}} Secured over \textbf{\textcolor{highlight}{1.2 million USD}} across \textbf{\textcolor{highlight}{seven}} grants, including a Google Research Scholar Award and the ABB Research Award (300,000 USD)---the largest endowment by a commercial organization for early-career researchers.
\item \textcolor{accent}{\textbf{Publications:}} Published in flagship venues such as ACM MobiCom, MobiSys, SenSys, IEEE/ACM Transactions on Networking, and IMWUT. Received a Best Paper Award and multiple Best Demonstration Awards.
\item \textcolor{accent}{\textbf{Industry Impact:}} International Patent Application (Sole Inventor) cited as foundational prior art by \textbf{\textcolor{highlight}{14+}} patents from Nokia, Vivo Mobile, KAIST, and Oppo. Research featured in press releases by ABB and Google.
\item \textcolor{accent}{\textbf{Teaching:}} Courses in embedded systems and wireless networking.
\item \textcolor{accent}{\textbf{Service:}} Served as a reviewer and program committee member for top-tier international conferences in mobile computing, networking, and sensing (ACM SenSys, MobiSys, IEEE INFOCOM, ACM IMC). Organized and chaired sessions at major conferences with hundreds of attendees (ACM EWSN, ACM/IEEE IPSN, IEEE RFID).
\end{itemize}}

\section{Experience}

\cvitem{2022--Present}{\textbf{National University of Singapore}}
\cvitem{}{Assistant Professor}
\cvitem{}{Department of Computer Science}
\cvitem{}{School of Computing}
\cvitem{}{}

\cvitem{2020--2022}{\textbf{University of California, Berkeley}}
\cvitem{}{Postdoctoral Scholar}
\cvitem{}{Mentor: Prof.\ Prabal Dutta}
\cvitem{}{}

\cvitem{2021}{\textbf{Royal Institute of Technology (KTH)}}
\cvitem{}{Visiting Researcher (on leave from UC Berkeley)}
\cvitem{}{}

\cvitem{2018--2020}{\textbf{Uppsala University}}
\cvitem{}{Postdoctoral Scholar}
\cvitem{}{}

\cvitem{2012}{\textbf{NXP Semiconductors}}
\cvitem{}{Software Engineer}
\cvitem{}{Embedded Wireless Networks / Low-Power Wireless Group}
\cvitem{}{}

\cvitem{2011--2012}{\textbf{Dhirubhai Ambani Institute of ICT}}
\cvitem{}{Research Engineer}
\cvitem{}{Networked Embedded Systems Lab}
\cvitem{}{Mentor: Prof.\ Prabhat Ranjan (Ph.D., UC Berkeley, 1986)}

\section{Education}

\cvitem{2012--2018}{\textbf{Ph.D., Computer Science}}
\cvitem{}{Uppsala University}
\cvitem{}{Dissertation: \large\textcolor{accent}{\textit{Enabling Sustainable Networked Embedded Systems}}}
\cvitem{}{\small Advisor: Prof.\ Thiemo Voigt (Uppsala University and RI.SE SICS, Sweden)}
\cvitem{}{\small Co-advisor: Prof.\ Luca Mottola (Politecnico di Milano, Italy and RI.SE SICS, Sweden)}
\cvitem{}{\small Opponent: Prof.\ Prabal Dutta (University of California, Berkeley, USA)}
\vspace{0.5em}
\cvitem{}{\textcolor{highlight}{\textbf{Dissertation awarded the ABB Research Award in Honor of Hubertus von Gr\"{u}nberg.}}}
\cvitem{}{\small Selection rate: approximately 1 in 60.}
\cvitem{}{\small Endowment of 300,000 USD.}
\cvitem{}{}

\cvitem{2007--2011}{\textbf{B.Tech., Information and Communication Technology}}
\cvitem{}{Dhirubhai Ambani Institute of Information and Communication Technology}

\input{sections/grants}
\input{sections/awards}
\input{sections/phd}
\input{sections/master}
\input{sections/ugurop}
\input{sections/ug}
\input{sections/talks}
\input{sections/pc}
\input{sections/selected}
\input{sections/full}
\input{sections/shortpubs}

\end{document}
