\newpage
\section{Awards}

\cvitem{2024}{\textbf{Google Research Scholar Award}.}
\cvitem{}{\textit{From Supply Chains to Personal Belongings: Designing Zero-Battery Trackers}.}
\cvitem{}{\textcolor{highlight}{\textbf{The only faculty member outside North America awarded in the Systems and Networking category for this year.}}}
\cvitem{}{}

\cvitem{2024}{\textbf{Best Demonstration Award (Runner-up)}.}
\cvitem{}{ACM/IEEE International Conference on Information Processing in Sensor Networks.}
\cvitem{}{\small\textcolor{accent}{ACM/IEEE IPSN.}}
\cvitem{}{}

\cvitem{2023}{\textbf{Best Demonstration Award}.}
\cvitem{}{ACM International Conference on Mobile Systems, Applications, and Services.}
\cvitem{}{\small\textcolor{accent}{ACM MobiSys.}}
\cvitem{}{}

\cvitem{2021}{\textbf{FORM+FUND Fellow}.}
\cvitem{}{University of California, Berkeley (Spring Cohort).}
\cvitem{}{}

\cvitem{2019}{\textbf{ABB Research Award in Honor of Hubertus von Gr\"{u}nberg}.}
\cvitem{}{Recipient of a 300,000 USD endowment.}
\cvitem{}{Awarded by Peter Voser (Chairman/CEO of ABB).}
\cvitem{}{\emph{Largest commercial endowment for early-career researchers.}}
\cvitem{}{}

\cvitem{2019}{\textbf{Attractive Innovation Project}.}
\cvitem{}{Uppsala University Innovation (Selected as Top 15 Project).}
\cvitem{}{}

\cvitem{2018}{\textbf{Breakthrough Ideas Grant}.}
\cvitem{}{Swedish Innovation Agency (Vinnova).}
\cvitem{}{}

\cvitem{2018}{\textbf{Best Demonstration Award}.}
\cvitem{}{ACM Conference on Security and Privacy in Wireless and Mobile Networks.}
\cvitem{}{\small\textcolor{accent}{ACM WiSec.}}
\cvitem{}{}

\cvitem{2017}{\textbf{Best Paper Award}.}
\cvitem{}{ACM Workshop on Visible Light Communication Systems, co-located with MobiCom.}
\cvitem{}{\small\textcolor{accent}{ACM VLCS.}}

\newpage
\section{Honors to Mentored Students}

\cvitem{}{\small Symbols: \phd~doctoral (Ph.D.) student, \pg~master's student, \ug~undergraduate student.}
\vspace{1em}
\cvitem{2025}{\textbf{Rising Star}.}
\cvitem{}{Awarded to mentee Rajashekar Reddy Chinthalapani\phd.}
\cvitem{}{ACM International Conference on Mobile Systems, Applications, and Services.}
\cvitem{}{\small\textcolor{accent}{ACM MobiSys.}}
\cvitem{}{}

\cvitem{2024}{\textbf{NUS Computing Innovation Prize}.}
\cvitem{}{Awarded to mentee Nobel Ang\ug.}
\cvitem{}{For Best Undergraduate Thesis.}
\cvitem{}{Selected by NUS and Singapore Computer Society.}
\cvitem{}{}

\cvitem{2023}{\textbf{Winner, Undergraduate Category}.}
\cvitem{}{Awarded to mentees Moteen Shah\ug{} (visiting from VJTI) and Adithya Bijoy\ug{} (visiting from IITD).}
\cvitem{}{ACM Student Research Competition (SRC) at MobiCom.}
\cvitem{}{\small\textcolor{accent}{ACM MobiCom.}}
\cvitem{}{}

\cvitem{2023}{\textbf{Third Place, Undergraduate Category}.}
\cvitem{}{Awarded to mentee Steven Waskito\ug.}
\cvitem{}{ACM Student Research Competition (SRC) at MobiCom.}
\cvitem{}{\small\textcolor{accent}{ACM MobiCom.}}
\cvitem{}{}

\cvitem{2023}{\textbf{Best Demonstration Award}.}
\cvitem{}{Awarded to mentee Wenqing Yan\phd.}
\cvitem{}{ACM International Conference on Mobile Systems, Applications, and Services.}
\cvitem{}{\small\textcolor{accent}{ACM MobiSys.}}
\cvitem{}{}

\cvitem{2021}{\textbf{N\textsuperscript{2}Women Young Researcher Fellowship}.}
\cvitem{}{Awarded to mentee Wenqing Yan\phd.}
\cvitem{}{}

\cvitem{2020}{\textbf{Best Ph.D.\ Forum Award}.}
\cvitem{}{Awarded to mentee Wenqing Yan\phd.}
\cvitem{}{ACM Conference on Embedded Networked Sensor Systems.}
\cvitem{}{\small\textcolor{accent}{ACM SenSys.}}
\cvitem{}{}

\cvitem{2017}{\textbf{Winner, Graduate Category}.}
\cvitem{}{Awarded to mentee Andreas Soleiman\pg.}
\cvitem{}{ACM Student Research Competition (SRC) at MobiCom.}
\cvitem{}{\small\textcolor{accent}{ACM MobiCom.}}
