\newpage
\sectionleft{Full Publications in Journals, Conferences, and Workshops}

Symbols next to author names indicate the enrollment status of students: \postdoc~postdoctoral scholar, \phd~doctoral (Ph.D.) student, \pg~master's student, and \ug~undergraduate student. Only students and scholars directly mentored by me are marked.

\begin{enumerate}

% ===================== 2025 =====================

\item Sooriya Patabandige Pramuka Medaranga\phd, Rajashekar Reddy Chinthalapani\phd, Wenqing Yan\phd, Prabal Dutta, \underline{Ambuj Varshney}.
\emph{Unraveling the Missing Link in Low-Power Communication: An Autodyning Receiver Architecture that Achieves a Long Range}.
In Proceedings of the 23rd Annual International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), 2025.

\item C. Rajashekar Reddy\phd, Dhairya Shah\phd, Nobel Ang\ug, \underline{Ambuj Varshney}.
\emph{AudioCast: Enabling Ubiquitous Connectivity for Embedded Systems through Audio-broadcasting Low-power Tags}.
Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies (\conf{PACM IMWUT}), 2025.

% ===================== 2024 =====================

\item Kunjun Li\ug, Manoj Gulati\postdoc, Dhairya Shah\phd, Steven Waskito\ug, Shantanu Chakrabarty, \underline{Ambuj Varshney}.
\emph{PixelGen: Rethinking Embedded Cameras for Mixed-Reality}.
In Proceedings of the 30th Annual International Conference on Mobile Computing and Networking (\conf{ACM IMMERCOM 2024 co-located with  MOBICOM}), 2024.

\item Lim Chang Quan Thaddeus\ug, C. Rajashekar Reddy\phd, Yuvraj Singh Bhadauria\ug, Dhairya Shah\phd, Manoj Gulati\postdoc, \underline{Ambuj Varshney}.
\emph{TunnelSense: Low-Power, Non-Contact Sensing Using Tunnel Diodes}.
In Proceedings of the IEEE International Conference on RFID (\conf{IEEE RFID}), 2024.

\item Muhammad  Mir, Borja Genoves Guzman, \underline{Ambuj Varshney}, Domenico Giustiniano. 
\emph{LiFi for Low-Power and Long-Range RF Backscatter}. 
IEEE/ACM Transactions on Networking (\conf{IEEE/ACM TON}), 2024.

% ===================== 2023 =====================

\item C. Rajashekar Reddy\phd, Manoj Gulati\postdoc, \underline{Ambuj Varshney}.
\emph{Beyond Broadcasting: Revisiting FM Frequency-band for Providing Connectivity to Next Billion Devices}.
In Proceedings of the 11th International Workshop on Energy Harvesting \& Energy-Neutral Sensing Systems (ENSsys), co-located with \conf{ACM SENSYS}, 2023.

\item Muhammad Sarmad Mir, Wenqing Yan\phd, Prabal Dutta, Domenico Giustiniano, \underline{Ambuj Varshney}.
\emph{TunnelLiFi: Bringing LiFi to Commodity Internet of Things Devices}.
In Proceedings of the 24th International Workshop on Mobile Computing Systems and Applications (\conf{ACM HOTMOBILE}), 2023.

% ===================== 2022 =====================

\item \underline{Ambuj Varshney}, Wenqing Yan\phd, Prabal Dutta.
\emph{Judo: Addressing the Energy Asymmetry of Wireless Embedded Systems through Tunnel Diode-Based Wireless Transmitters}.
In Proceedings of the 20th ACM International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), 2022.

\item \underline{Ambuj Varshney}. 
\emph{Making Low-Power and Long-Range Wireless Backscatter Transmitters}. 
GetMobile: Mobile Computing and Communications (\conf{ACM GETMOBILE}), 2022.

% ===================== 2021 =====================

\item Muhammad Sarmad, Borja Genoves, \underline{Ambuj Varshney}, Domenico Giustiniano. 
\emph{PassiveLiFi: Rethinking LiFi for Low-Power and Long-Range RF Backscatter}. 
In Proceedings of the 27th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2021.

\item Revathy Narayanan, \underline{Ambuj Varshney}, Panos Papadimitratos. 
\emph{Securing Battery-Free Backscatter Tags through Fingerprinting}. 
In Proceedings of the 20th ACM Workshop on Hot Topics in Networks (\conf{ACM HotNets}), 2021.

% ===================== 2020 =====================

\item \underline{Ambuj Varshney}, Lorenzo Corneo. 
\emph{Tunnel Emitter: Tunnel Diode-Based Low-Power Carrier Emitters for Backscatter Tags}. 
In Proceedings of the 26th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2020.

\item \underline{Ambuj Varshney}\textsuperscript{*}, Ander Galisteo\textsuperscript{*}, Domenico Giustiniano. 
\emph{Two to Tango: Hybrid Light and Backscatter Networks for Next Billion Devices}. 
In Proceedings of the 18th ACM International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), 2020.\\
\textbf{*Co-primary authors contributing equally.}

% ===================== 2019 =====================

\item \underline{Ambuj Varshney}, Andreas Soleiman\pg, Thiemo Voigt.
\emph{TunnelScatter: Enabling Low-Power Communication for Sensor Tags Using Tunnel Diodes}.
In Proceedings of the 25th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2019.

\item \underline{Ambuj Varshney}. 
\emph{Position: Wearable Polymorphic Light Sensors}. 
In Proceedings of the 5th ACM Workshop on Wearable Systems and Applications (\conf{ACM WEARSYS}), co-located with \conf{ACM MOBISYS}, 2019.

% ===================== 2018 =====================

\item Domenico Giustiniano, \underline{Ambuj Varshney}, Thiemo Voigt. 
\emph{Connecting Battery-Free IoT Tags Using LED Bulbs}. 
In Proceedings of the 17th ACM Workshop on Hot Topics in Networks (\conf{ACM HotNets}), 2018.

% ===================== 2018 =====================

\item Carlos Perez Penichet, Claro Noda, \underline{Ambuj Varshney}, Thiemo Voigt. 
\emph{Battery-Free 802.15.4 Receiver}. 
In Proceedings of the 17th International Conference on Information Processing in Sensor Networks (\conf{ACM/IEEE IPSN}), 2018.

% ===================== 2017 =====================

\item \underline{Ambuj Varshney}, Oliver Harms\pg, Carlos Perez Penichet, Christian Rohner, Frederik Hermans, Thiemo Voigt.
\emph{LoRea: A Backscatter Architecture that Achieves a Long Communication Range}.
In Proceedings of the 15th ACM Conference on Embedded Networked Sensor Systems (\conf{ACM SENSYS}), 2017.

\item \underline{Ambuj Varshney}, Andreas Soleiman\pg, Luca Mottola, Thiemo Voigt.
\emph{Battery-Free Visible Light Sensing}.
In Proceedings of the 4th ACM Workshop on Visible Light Communication Systems (\conf{ACM VLCS}), co-located with \conf{ACM MOBICOM}, 2017.

\item \underline{Ambuj Varshney}, Carlos Perez Penichet, Christian Rohner, Thiemo Voigt. 
\emph{Towards Wide-Area Backscatter Networks}. 
In Proceedings of the 4th ACM Workshop on Hot Topics in Wireless, co-located with \conf{ACM MOBICOM}, 2017.

% ===================== 2016 =====================

\item Kasun Hewage, \underline{Ambuj Varshney}, Abdullah Hylamia\ug, Thiemo Voigt.
\emph{modBulb: A Modular Light Bulb for Visible Light Communication}.
In Proceedings of the 3rd ACM Workshop on Visible Light Communication Systems (\conf{ACM VLCS}), co-located with \conf{ACM MOBICOM}, 2016.

\item Carlos Pérez-Penichet, \underline{Ambuj Varshney}, Frederik Hermans, Christian Rohner, Thiemo Voigt. 
\emph{Do Multiple Bits per Symbol Increase the Throughput of Ambient Backscatter Communications?} 
In Proceedings of the International Workshop on New Wireless Communication Paradigms for the Internet of Things (MadCom), co-located with EWSN, 2016.

\item Carlos Perez Penichet, Frederik Hermans, \underline{Ambuj Varshney}, Thiemo Voigt. 
\emph{Augmenting IoT Networks with Backscatter-Enabled Passive Sensor Tags}. 
In Proceedings of the 3rd ACM Workshop on Hot Topics in Wireless, co-located with \conf{ACM MOBICOM}, 2016.

% ===================== 2015 =====================

\item \underline{Ambuj Varshney}, Luca Mottola, Mats Carlsson, Thiemo Voigt. 
\emph{Directional Transmissions and Receptions for High-Throughput Bulk Forwarding in Wireless Sensor Networks}. 
In Proceedings of the 13th ACM Conference on Embedded Networked Sensor Systems (\conf{ACM SENSYS}), 2015.

\item Bo Wei, \underline{Ambuj Varshney}, Wen Hu, Neal Patwari, Thiemo Voigt, Chun Tung Chou. 
\emph{dRTI: Directional Radio Tomographic Imaging}. 
In Proceedings of the 14th International Conference on Information Processing in Sensor Networks (\conf{ACM/IEEE IPSN}), 2015.

% ===================== 2013 =====================

\item \underline{Ambuj Varshney}, Luca Mottola, Thiemo Voigt. 
\emph{Using Directional Transmissions and Receptions to Reduce Contention in Wireless Sensor Networks}. 
In Proceedings of the 5th International Workshop on Real-World Wireless Sensor Networks (REALWSN), 2013.

\item Juan M. Alonso, Thiemo Voigt, \underline{Ambuj Varshney}. 
\emph{Bounds on the Lifetime of Wireless Sensor Networks}. 
In Proceedings of the 5th International Workshop on Performance Control in Wireless Sensor Networks, co-located with IEEE DCOSS, 2013.

\end{enumerate}