\newpage
\section{Research Grants}

\cvitem{2024}{\textbf{From Supply Chains to Personal Belongings: Designing Zero-Battery Trackers}.}
\cvitem{}{Google Research Scholar Award.}
\cvitem{}{Role: Principal Investigator (Sole PI).}
\cvitem{}{Amount: \textcolor{accent}{35,000 USD (Unrestricted Gift)}.}
\cvitem{}{}

\cvitem{2023--2026}{\textbf{Tackling the Challenge of Energy-Efficient Reception to Enable the Next Billion IoT Devices}.}
\cvitem{}{Ministry of Education (Singapore) Tier 1 Grant.}
\cvitem{}{Role: Principal Investigator (Sole PI).}
\cvitem{}{Amount: \textcolor{accent}{250,000 SGD}.}
\cvitem{}{}

\cvitem{2022--2025}{\textbf{Enabling Continuous, Real-time Monitoring of Human Vitals through Battery-free Tunnel Diode Sensors}.}
\cvitem{}{NUS ARTIC Center.}
\cvitem{}{Role: Principal Investigator (Sole PI).}
\cvitem{}{Amount: \textcolor{accent}{214,000 SGD}.}
\cvitem{}{}

\cvitem{2022--2024}{\textbf{Enabling Non-Intrusive Monitoring of Internet of Things}.}
\cvitem{}{NUS-NCS Joint Center.}
\cvitem{}{Role: Principal Investigator (PI) with Co-PI Shantanu (NCS).}
\cvitem{}{Amount: \textcolor{accent}{465,000 SGD}.}
\cvitem{}{}

\cvitem{2022--2026}{\textbf{Enabling Sustainable and Large-Scale Wireless Networks of Embedded Systems}.}
\cvitem{}{NUS ODPRT (Start-up Grant).}
\cvitem{}{Role: Principal Investigator (Sole PI).}
\cvitem{}{Amount: \textcolor{accent}{250,000 SGD}.}
\cvitem{}{}

\cvitem{2019--2022}{\textbf{Towards Future Factories: Enabling Sustainable Sensing}.}
\cvitem{}{ABB Research Award in Honor of Hubertus von Gr\"{u}nberg.}
\cvitem{}{Role: Awardee (Hosted at UC Berkeley).}
\cvitem{}{Amount: \textcolor{accent}{300,000 USD}.}
\cvitem{}{}

\cvitem{2018--2019}{\textbf{Enabling Factories of the Future Using Sustainable Sensing}.}
\cvitem{}{VINNOVA (Swedish Innovation Agency).}
\cvitem{}{Role: Principal Investigator (Sole PI).}
\cvitem{}{Hosted at Uppsala University.}
\cvitem{}{Amount: \textcolor{accent}{499,000 SEK (approx.\ 50,000 USD)}.}
