\newpage
\section{Master's Supervision}

\subsection{Current Students (National University of Singapore)}

\cvitem{2025--Present}{\textbf{Tikyi Min Khant Naing}.}
\cvitem{}{\small\textcolor{gray}{Exploring machine learning (TinyML) on embedded devices.}}
\cvitem{}{}

\cvitem{2025--Present}{\textbf{Meng Xianyu}.}
\cvitem{}{\small\textcolor{gray}{Rethinking Embedded Cameras Using Image and Language Models.}}
\cvitem{}{}

\cvitem{2025--Present}{\textbf{Li Shuaixian}.}
\cvitem{}{\small\textcolor{gray}{Rethinking Embedded Cameras Using Image and Language Models.}}

\vspace{1em}
\noindent\hspace{\hintscolumnwidth}\hspace{\separatorcolumnwidth}\rule{\maincolumnwidth}{0.4pt}
\subsection{Alumni (National University of Singapore)}

\cvitem{2025}{\textbf{Andre Teo Ser Yeong}.}
\vspace{0.7em}
\cvitem{2025}{\textbf{Huang Keyi}.}
\vspace{0.7em}
\cvitem{2025}{\textbf{Dennis Patrick Warfield}.}
\vspace{0.7em}
\cvitem{2024}{\textbf{Henrikus Theorizchy Cleven}.}
\vspace{0.7em}
\cvitem{2024}{\textbf{Hew Sock Fang}.}
\vspace{0.7em}
\cvitem{2024}{\textbf{Wu Zihao}.}
\vspace{0.7em}
\cvitem{2024}{\textbf{Chee Han Quan, Edison}.}
\vspace{0.7em}
\cvitem{2023}{\textbf{Qiao Yukai}.}
\vspace{0.7em}
\cvitem{2023}{\textbf{Yusril Izza}.}
\vspace{0.7em}
\cvitem{2023}{\textbf{Goh Sheen An}.}
\cvitem{}{\emph{Current: Lead Software Engineer, GovTech Singapore.}}
\vspace{0.7em}
\cvitem{2023}{\textbf{Lim Soon Lee}.}
\cvitem{}{\emph{Current: MINDEF.}}

\newpage
\vspace{1em}
\noindent\hspace{\hintscolumnwidth}\hspace{\separatorcolumnwidth}\rule{\maincolumnwidth}{0.4pt}
\subsection{Alumni (Uppsala University)}

\cvitem{2017--2019}{\textbf{Andreas Soleiman}.}
\cvitem{}{\small\textcolor{gray}{Battery-free Visible Light Sensing.}}
\cvitem{}{\emph{Placement: Ph.D.\ Student at MIT (Prof.\ Fadel Adib).}}
\cvitem{}{}

\cvitem{2018}{\textbf{Sam Hilamia}.}
\cvitem{}{\small\textcolor{gray}{Battery-free Radio Tomographic Imaging.}}
\cvitem{}{\emph{Placement: Ph.D.\ Student at Uppsala University.}}
\cvitem{}{}

\cvitem{2018}{\textbf{Gustav Eriksson}.}
\cvitem{}{\small\textcolor{gray}{Towards Long-Range Backscatter Communication Using Tunnel Diode Amplifiers.}}
\cvitem{}{\emph{Placement: Engineer at Intertek Semko.}}
\cvitem{}{}

\cvitem{2016--2017}{\textbf{Oliver Harms}.}
\cvitem{}{\small\textcolor{gray}{Modulation Schemes in Ambient Backscatter Communication.}}
\cvitem{}{\emph{Placement: Ph.D.\ Student at Chalmers University.}}
\cvitem{}{}

\cvitem{2016}{\textbf{Elena Di Lascio}.}
\cvitem{}{\small\textcolor{gray}{A Battery-free Indoor Localization System.}}
\cvitem{}{\emph{Placement: Ph.D.\ Student at USI Lugano, Switzerland.}}
