\newpage
\section{Postdoctoral and Doctoral Supervision}

\subsection{Doctoral Students (Current)}

\cvitem{2023--2027}{\textbf{Pramuka Sooriyapatabandige} (NUS).}
\cvitem{}{Role: Sole primary advisor.}
\cvitem{}{}

\cvitem{2023--2027}{\textbf{Chinthalapani Rajashekar Reddy} (NUS).}
\cvitem{}{Role: Sole primary advisor.}
\cvitem{}{}

\cvitem{2023--2028}{\textbf{Kandala Savitha Viswanadh} (NUS).}
\cvitem{}{Role: Sole primary advisor.}
\cvitem{}{}

\cvitem{2024--2028}{\textbf{Dhairya Shah} (NUS).}
\cvitem{}{Role: Sole primary advisor.}
\cvitem{}{}

\cvitem{2026--2030}{\textbf{Spanddhana Sara} (NUS).}
\cvitem{}{Role: Sole primary advisor.}
\cvitem{}{}

\cvitem{2025--2030}{\textbf{Anna Seiderer} (Uppsala University).}
\cvitem{}{Role: Co-supervisor (with Prof.\ Christian Rohner).}

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}
\subsection{Postdoctoral Researchers (Alumni)}

\cvitem{2025--2026}{\textbf{Dr.\ Amalinda Gamage}.}
\cvitem{}{Background: Ph.D., Nanyang Technological University (with Prof.\ Mo Li).}
\cvitem{}{}

\cvitem{2023--2024}{\textbf{Dr.\ Manoj Gulati}.}
\cvitem{}{Background: Ph.D., IIIT Delhi.}
\cvitem{}{Visiting Scholar at University of Washington (with Prof.\ Shwetak Patel).}
\cvitem{}{\emph{Placement: Principal Application Engineer, Western Digital.}}

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}
\subsection{Doctoral Students (Alumni)}

\cvitem{2018--2024}{\textbf{Dr.\ Wenqing Yan} (Uppsala University).}
\cvitem{}{Co-supervised with Prof.\ Christian Rohner and Prof.\ Thiemo Voigt.}
\cvitem{}{Thesis: \textit{Design and Identification of Wireless Transmitters for a Low-Power and Secure IoT}.}
\cvitem{}{Opponent: Prof.\ Haitham Hassanieh (EPFL).}
\cvitem{}{Committee: Prof.\ Niki Trigoni (Oxford), Prof.\ Danny Hughes (KU Leuven).}
\cvitem{}{\emph{Placement: Experienced Researcher, Ericsson Research, Sweden.}}
