\newpage
\section{Selected Publications}

\cvitem{}{Symbols next to author names indicate the enrollment status of students: \postdoc~postdoctoral scholar, \phd~doctoral (Ph.D.) student, \pg~master's student, and \ug~undergraduate student. Only students and scholars directly mentored by me are marked.}

\cvitem{2025}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3729471}{AudioCast: Enabling Ubiquitous Connectivity for Embedded Systems through Audio-Broadcasting Low-Power Tags}}.
Rajashekar Reddy Chinthalapani\phd, Dhairya Jigar Shah\phd, Nobel Ang\ug, and \underline{Ambuj Varshney}.
\textcolor{blue}{ACM IMWUT 2025 / UbiComp 2025}.}

\vspace{0.3em}

\cvitem{}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3711875.3729164}{Unraveling the Missing Link in Low-Power Communication: An Autodyning Receiver that Achieves a Long Range}}.
Sooriya Patabandige Pramuka Medaranga\phd, Rajashekar Reddy Chinthalapani\phd, Wenqing Yan\phd, Prabal Dutta, and \underline{Ambuj Varshney}.
\textcolor{blue}{ACM MobiSys 2025}.}

\vspace{1em}

\cvitem{2024}{%
\emph{\href{https://doi.org/10.1109/TNET.2023.3344316}{LiFi for Low-Power and Long-Range RF Backscatter}}.
Muhammad Sarmad Mir, Borja G.\ Guzman, \underline{Ambuj Varshney}, and Domenico Giustiniano.
\textcolor{blue}{IEEE/ACM Transactions on Networking, Vol.\ 32, No.\ 3, 2024}.}

\vspace{0.3em}

\cvitem{}{%
\emph{\href{https://doi.org/10.1109/RFID62091.2024.10582671}{TunnelSense: Low-Power, Non-Contact Sensing Using Tunnel Diodes}}.
L.\,C.\,Q.\ Thaddeus\ug, C.\,R.\ Reddy\phd, Y.\,S.\ Bhadauria\ug, Dhairya Jigar Shah\phd, M.\ Gulati\postdoc, and \underline{Ambuj Varshney}.
\textcolor{blue}{IEEE RFID 2024}.}

\vspace{0.3em}

\cvitem{}{%
\emph{\href{https://doi.org/10.1145/3636534.3696216}{PixelGen: Rethinking Embedded Cameras for Mixed-Reality}}.
Kunjun Li\ug, Manoj Gulati\postdoc, Dhairya Jigar Shah\phd, Steven Waskito\ug, Shantanu Chakrabarty, and \underline{Ambuj Varshney}.
\textcolor{blue}{ACM ImmerCom 2024 (co-located with MobiCom)}.\newline
\textcolor{magenta!70!black}{\textbf{Best Demonstration Runner-up, ACM/IEEE IPSN 2024.}}}

\vspace{1em}

\cvitem{2023}{%
\emph{\href{https://doi.org/10.1145/3628353.3628546}{Beyond Broadcasting: Revisiting FM Frequency-Band for Providing Connectivity to Next Billion Devices}}.
C.\ Rajashekar Reddy\phd, Manoj Gulati\postdoc, and \underline{Ambuj Varshney}.
\textcolor{blue}{ACM ENSsys 2023 (co-located with ACM SenSys)}.}

\vspace{0.3em}

\cvitem{}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3572864.3580327}{TunnelLiFi: Bringing LiFi to Commodity Internet of Things Devices}}.
Muhammad Sarmad Mir, Wenqing Yan\phd, Prabal Dutta, Domenico Giustiniano, and \underline{Ambuj Varshney}.
\textcolor{blue}{ACM HotMobile 2023}.}

\vspace{1em}

\cvitem{2022}{%
\emph{\href{https://doi.org/10.1145/3551670.3551672}{Making Low-Power and Long-Range Wireless Backscatter Transmitters}}.
\underline{Ambuj Varshney}.
\textcolor{blue}{ACM GetMobile 2022}.
\textcolor{magenta!70!black}{\textbf{Invited Contribution.}}}

\vspace{0.3em}

\cvitem{}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3498361.3538923}{Judo: Addressing the Energy Asymmetry of Wireless Embedded Systems through Tunnel Diode-Based Wireless Transmitters}}.
\underline{Ambuj Varshney}, Wenqing Yan\phd, and Prabal Dutta.
\textcolor{blue}{ACM MobiSys 2022}.}

\vspace{1em}

\cvitem{2021}{%
\emph{Radio Frequency Communication Device for Low-Power Communication}.
Inventor: \underline{Ambuj Varshney} (Sole Inventor).
\textcolor{blue}{International Patent Application (PCT): WO2021040594A1}.\newline
\textcolor{magenta!70!black}{\textbf{Industry Impact:} Cited as foundational prior art by 14+ patents from industry and academic leaders, including Nokia, Vivo Mobile, KAIST, and Oppo.}}

\vspace{1em}

\cvitem{2020}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3372224.3419199}{Tunnel Emitter: Tunnel Diode-Based Low-Power Carrier Emitters for Backscatter Tags}}.
\underline{Ambuj Varshney} and Lorenzo Corneo.
\textcolor{blue}{ACM MobiCom 2020}.}

\vspace{0.3em}

\cvitem{}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3386901.3388918}{Two to Tango: Hybrid Light and Backscatter Networks for Next Billion Devices}}.
\underline{Ambuj Varshney}\textsuperscript{*}, Ander Galisteo\textsuperscript{*}, and Domenico Giustiniano.
\textcolor{blue}{ACM MobiSys 2020}.\newline
\textbf{*Co-primary authors contributing equally.}}

\vspace{1em}

\cvitem{2019}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3300061.3345451}{TunnelScatter: Enabling Low-Power Communication for Sensor Tags Using Tunnel Diodes}}.
\underline{Ambuj Varshney}, Andreas Soleiman\pg, and Thiemo Voigt.
\textcolor{blue}{ACM MobiCom 2019}.}

\vspace{1em}

\cvitem{2017}{%
\emph{\href{https://dl.acm.org/doi/10.1145/3129881.3129890}{Battery-Free Visible Light Sensing}}.
\underline{Ambuj Varshney}, Andreas Soleiman\pg, Luca Mottola, and Thiemo Voigt.
\textcolor{blue}{ACM VLCS 2017 (co-located with MobiCom)}.\newline
\textbf{Best Paper Award.}}

\vspace{0.3em}

\cvitem{}{%
\emph{\href{https://dl.acm.org/citation.cfm?id=3131691}{LoRea: A Backscatter Architecture that Achieves a Long Communication Range}}.
\underline{Ambuj Varshney}, Oliver Harms\pg, Carlos Perez Penichet, Christian Rohner, Frederik Hermans, and Thiemo Voigt.
\textcolor{blue}{ACM SenSys 2017}.}

\vspace{1em}

\cvitem{2015}{%
\emph{\href{https://dl.acm.org/doi/10.1145/2809695.2809720}{Directional Transmissions and Receptions for High-Throughput Bulk Forwarding in Wireless Sensor Networks}}.
\underline{Ambuj Varshney}, Luca Mottola, Mats Carlsson, and Thiemo Voigt.
\textcolor{blue}{ACM SenSys 2015}.}
