\newpage
\sectionleft{Posters, Demonstrations, and Short Publications}

The following are peer-reviewed short publications (posters and demonstrations) published as part of conference proceedings.

Symbols next to author names indicate the enrollment status of students: \postdoc~postdoctoral scholar, \phd~doctoral (Ph.D.) student, \pg~master's student, and \ug~undergraduate student. Only students and scholars directly mentored by me are marked.

\begin{enumerate}

% ===================== 2025 =====================

\item Dhairya Shah\phd, Rajashekar Reddy Chinthalapani\phd, \underline{Ambuj Varshney}. 
\emph{Poster: Enabling Low-power Ubiquitous Connectivity for Embedded Systems through Audio-Broadcasting Tags}.\\
In Companion of the ACM International Joint Conference on Pervasive and Ubiquitous Computing (\conf{ACM UBICOMP}), 2026.

\item Celes Chai Jia Xuan\ug, Dhairya Shah\phd, \underline{Ambuj Varshney}. 
\emph{Demo: VisibleBits: Illuminating Mixed Reality with Li-Fi Information Spotlights}. 
In Proceedings of the 31st Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2025.

\item Rajashekar Reddy Chinthalapani, Dhairya Shah\phd, \underline{Ambuj Varshney}. 
\emph{Demo: Enabling Ubiquitous Connectivity for Embedded Systems through Audio-Broadcasting Low-power Tags}. 
In Proceedings of the 23rd Annual International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), 2025.

% ===================== 2024 =====================

\item Moteen Shah\ug, Dhairya Shah\phd, Pramuka Medaranga\phd, \underline{Ambuj Varshney}. 
\emph{Poster: Li-FiAR: Networking Augmented-Reality Devices through Visible Light}. 
In Proceedings of the 30th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2024.

\item Savitha Viswanadh Kandala\phd, \underline{Ambuj Varshney}. 
\emph{Poster: A Framework for Training and Deploying Foundational Language Models for Embedded Sensing}. 
In Proceedings of the 30th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2024.

\item Sara Spanddhana\pg, Moteen Shah\ug, Dhairya Shah\phd, Rajashekar Reddy Chinthalapani, \underline{Ambuj Varshney}. 
\emph{Poster: GateHaul: A Gateway Architecture using Backhauling Networks to Address the Connectivity Challenges of Embedded Systems}. 
In Proceedings of the 30th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2024.

\item Pramuka Medaranga\phd, Dhairya Shah\phd, Savitha Viswanadh Kandala\phd, \underline{Ambuj Varshney}. 
\emph{Poster: Simplifying the Networking of Wireless Embedded Systems using a Large Language Model}. 
In Proceedings of the ACM SIGCOMM Conference: Posters and Demos (\conf{ACM SIGCOMM}), 2024.

\item Kunjun Li, Manoj Gulati, Dhairya Shah\phd, Steven Waskito, Shantanu Chakrabarty, \underline{Ambuj Varshney}. 
\emph{Demo Abstract: PixelGen: Rethinking Embedded Camera Systems for Mixed-Reality}. 
In Proceedings of the 23rd ACM/IEEE International Conference on Information Processing in Sensor Networks (\conf{ACM/IEEE IPSN}), 2024.

% ===================== 2023 =====================

\item Steven Waskito\ug, Kai Jie Leow\ug, Pramuka Medaranga\phd, Tejas Gupta\ug, Shantanu Chakrabarty, Manoj Gulati\postdoc, \underline{Ambuj Varshney}. 
\emph{Demo Abstract: Light and Vibration Gesture Sensing with OTTER: Embedded Data Collection and Analysis Using LLMs}. 
In Proceedings of the 21st ACM Conference on Embedded Networked Sensor Systems (\conf{ACM SENSYS}), 2023.

\item Steven Waskito\ug, Kai Jie Leow\ug, Pramuka Medaranga\phd, Tejas Gupta\ug, Shantanu Chakrabarty, Manoj Gulati\postdoc, \underline{Ambuj Varshney}. 
\emph{Poster: Otter: Simplifying Embedded Sensor Data Collection and Analysis using Large Language Models}. 
In Proceedings of the 29th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2023.

\item Dayrene Frometa Fonseca, Muhammad Sarmad Mir, Borja Genoves Guzman, \underline{Ambuj Varshney}, Domenico Giustiniano. 
\emph{Demo: PassiveLiFi Demonstration: Rethinking LiFi for Low-Power and Long Range RF Backscatter}. 
In Proceedings of the 29th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2023.

\item Moteen Amin Shah\ug, Adithya Bijoy\ug, Manoj Gulati\postdoc, Wenqing Yan\phd, \underline{Ambuj Varshney}. 
\emph{Poster: Going Beyond Backscatter: Rethinking Low-Power Wireless Transmitters using Tunnel Diodes}. 
In Proceedings of the 29th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2023.

\item Goh Sheen An\pg, \underline{Ambuj Varshney}. 
\emph{Poster: VoCopilot: Enabling Voice-Activated Tracking for Everyday Interactions}. 
In Proceedings of the 21st Annual International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), 2023.

\item Pramuka Medaranga\phd, Steven Waskito\ug, Kunjun Li\ug, Kai Jie Leow\ug, Shantanu Chakrabarty, \underline{Ambuj Varshney}. 
\emph{Poster: Rethinking Embedded Sensor Data Processing and Analysis with Large Language Models}. 
In Proceedings of the 21st Annual International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), 2023.

\item Tobias Mages, Wenqing Yan\phd, \underline{Ambuj Varshney}, Christian Rohner. 
\emph{Demo: An Educational Platform to Learn Radio Frequency Wireless Communication}. 
In Proceedings of the 21st Annual International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), 2023.

% ===================== 2022 =====================

\item Wenqing Yan\phd, \underline{Ambuj Varshney}. 
\emph{Poster: Enabling L3: Low Cost, Low Complexity and Low Power Radio Frequency Sensing Using Tunnel Diodes}. 
In Proceedings of the 28th Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2022.

% ===================== 2019 =====================

\item Andreas Soleiman\ug, \underline{Ambuj Varshney}. 
\emph{Poster: Towards Backscatter-enabled Networked Utensils}. 
In Proceedings of the 17th ACM International Conference on Mobile Systems, Applications, and Services (\conf{ACM MOBISYS}), Seoul, Korea, 2019.

% ===================== 2018 =====================

\item Abdullah Hylamia\pg, \underline{Ambuj Varshney}, Andreas Soleiman\ug, Panagiotis Papadimitratos, Christian Rohner, Thiemo Voigt. 
\emph{Demo: Towards Battery-free Radio Tomographic Imaging}. 
In Proceedings of the 11th ACM Conference on Security and Privacy in Wireless and Mobile Networks (\conf{ACM WISEC}), 2018.\\
\textcolor{red}{\textbf{Best Demonstration Award}}.

\item Abdullah Hylamia\pg, Marco Spanghero, \underline{Ambuj Varshney}, Thiemo Voigt, Panagiotis Papadimitratos. 
\emph{Demo: Security on Harvested Power}. 
In Proceedings of the 11th ACM Conference on Security and Privacy in Wireless and Mobile Networks (\conf{ACM WISEC}), 2018.

\item Carlos-Perez Penichet, Claro Noda, \underline{Ambuj Varshney}, Thiemo Voigt. 
\emph{Demo: Battery-free 802.15.4 Receiver}. 
In Proceedings of the 17th International Conference on Information Processing in Sensor Networks (\conf{ACM/IEEE IPSN}), 2018.

% ===================== 2017 =====================

\item Andreas Soleiman\ug, \underline{Ambuj Varshney}, Thiemo Voigt. 
\emph{Poster: Battery-free Visible Light Sensing}. 
In Proceedings of the 23rd Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2017.\\
\textcolor{red}{Student under my supervision won the \textbf{ACM SRC (Graduate) Winner}}.

\item Andreas Soleiman\ug, \underline{Ambuj Varshney}, Luca Mottola, Thiemo Voigt. 
\emph{Demo: Battery-free Visible Light Sensing}. 
In Proceedings of the 4th ACM Workshop on Visible Light Communication Systems (\conf{ACM VLCS}), co-located with \conf{ACM MOBICOM} 2017.

\item \underline{Ambuj Varshney}, Carlos Perez Penichet, Christian Rohner, Thiemo Voigt. 
\emph{Demo: LoRea: A Backscatter Architecture that Achieves a Long Communication Range}. 
In Proceedings of the 15th ACM Conference on Embedded Networked Sensor Systems (\conf{ACM SENSYS}), 2017.

\item Carlos Perez Penichet, Claro Noda, \underline{Ambuj Varshney}, Thiemo Voigt. 
\emph{Poster: Augmenting WSNs with Interoperable 802.15.4 Sensor Tags}. 
In Proceedings of the 15th ACM Conference on Embedded Networked Sensor Systems (\conf{ACM SENSYS}), 2017.

% ===================== 2016 =====================

\item Carlos Perez Penichet, Frederik Hermans, \underline{Ambuj Varshney}, Thiemo Voigt. 
\emph{Demo: Passive Sensor Tags}. 
In Proceedings of the 22nd Annual International Conference on Mobile Computing and Networking (\conf{ACM MOBICOM}), 2016.

\item Kasun Hewage, \underline{Ambuj Varshney}, Abdalah Hilamia\ug, Thiemo Voigt. 
\emph{modBulb: A Modular Light Bulb for Visible Light Communication}. 
In Proceedings of the 3rd ACM Workshop on Visible Light Communication Systems (\conf{ACM VLCS}), 2016.

\item Abdalah Hilmia\ug, Kasun Hewage, \underline{Ambuj Varshney}, Christian Rohner, Thiemo Voigt. 
\emph{BouKey: Location-based Key Sharing Using Visible Light Communication}. 
In Proceedings of the 15th International Conference on Information Processing in Sensor Networks (\conf{ACM/IEEE IPSN}), 2016.

\item Elena Di Lascio\pg, \underline{Ambuj Varshney}, Thiemo Voigt, Carlos Pérez-Penichet. 
\emph{LocaLight: A Battery-free Passive Localization System Using Visible Light}. 
In Proceedings of the 15th International Conference on Information Processing in Sensor Networks (\conf{ACM/IEEE IPSN}), 2016.

% ===================== 2015 =====================

\item \underline{Ambuj Varshney}, Luca Mottola, Thiemo Voigt. 
\emph{Coordination of Wireless Sensor Networks Using Visible Light}. 
In Proceedings of the 13th ACM Conference on Embedded Networked Sensor Systems (\conf{ACM SENSYS}), 2015.

% ===================== 2014 =====================

\item \underline{Ambuj Varshney}, Luca Mottola, Thiemo Voigt. 
\emph{Directional Transmissions and Receptions for Burst Forwarding Using Disjoint Paths}. 
In Proceedings of the 13th ACM/IEEE International Conference on Information Processing in Sensor Networks (\conf{ACM/IEEE IPSN}), 2014.

% ===================== 2013 =====================

\item \underline{Ambuj Varshney}, Luca Mottola, Thiemo Voigt. 
\emph{Directional Transmissions and Receptions for High Throughput Burst Forwarding}. 
In Proceedings of the 11th ACM Conference on Embedded Networked Sensor Systems (\conf{ACM SENSYS}), 2013.

\end{enumerate}