\section{Positions of Trust}

\cvitem{2025}{Internal Doctoral Examination, Ph.D.\ Oral Defense of Wu Dan, National University of Singapore.}
\cvitem{}{\small Advisor: Tulika Mitra.}
\cvitem{}{\small Committee: He Bingsheng, Ambuj Varshney, and Jialin Li (Head of Department Representative).}

\vspace{1em}
\cvitem{2025}{Internal Doctoral Examination, Ph.D.\ Oral Defense of Choi Inho, National University of Singapore.}
\cvitem{}{\small Advisor: Jialin Li.}
\cvitem{}{\small Committee: Ma Tianbai Richard, He Bingsheng, and Ambuj Varshney (Head of Department Representative).}

\vspace{1em}
\cvitem{2025}{Internal Doctoral Examination, Ph.D.\ Oral Defense of Yu Miao, National University of Singapore.}
\cvitem{}{\small Advisor: Trevor Carlson.}
\cvitem{}{\small Committee: Peh Li Shiuan, Wong Weng Fai, and Ambuj Varshney (Head of Department Representative).}

\vspace{1em}
\cvitem{2025}{External Examiner, Ph.D.\ Thesis of Cheng Jiang, \textit{Advancing Wireless Sensing in Granularity, Efficiency, and Generalization Across Diverse Wireless Technologies}, University of New South Wales (UNSW), Australia.}

\vspace{1em}
\cvitem{2022}{\href{https://new.abb.com/news/detail/95853/abb-announces-2022-awardee-for-abb-research-award-in-honor-of-hubertus-von-grunberg}{Jury Member, ABB Research Award in Honor of Hubertus von Gr\"{u}nberg.}}
\cvitem{}{\small Jury: Dr.\ Hubertus von Gr\"{u}nberg, Prof.\ Nina Thornhill (Imperial College London), Prof.\ Roland Siegwart (ETH Zurich), Prof.\ Manfred Morari (University of Pennsylvania), Dr.\ Ambuj Varshney (National University of Singapore), and Dr.\ Bernhard Eschermann (CTO, ABB Process Automation).}

\vspace{1em}
\cvitem{2020}{External Examiner, Ph.D.\ Thesis of Ander Galisteo, \textit{Visible Light Communication Networks for IoT and its Application}, Universidad Carlos III de Madrid, Spain.}

\vspace{1em}
\cvitem{}{Reviewer of Grant, Advanced Research and Technology Innovation Centre (ARTIC), National University of Singapore.}
