\newpage
\section{Undergraduate Supervision (Final Year Projects)}

\subsection{Academic Year 2024/2025}

\cvitem{}{\textbf{Wang Minhong}.}
\cvitem{}{\small\textcolor{gray}{Building an Embedded Operating System (Tiku).}}
\cvitem{}{}
\cvitem{}{\textbf{Fu Yiqiao}.}
\cvitem{}{\small\textcolor{gray}{Building an Embedded Operating System (Tiku).}}
\cvitem{}{}
\cvitem{}{\textbf{Sean Wang}.}
\cvitem{}{\small\textcolor{gray}{Earth Computers.}}
\cvitem{}{}
\cvitem{}{\textbf{Daniel Goh Chin Hao}.}
\cvitem{}{\small\textcolor{gray}{Backhauling Networks and Internet of Things.}}
\cvitem{}{}
\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}
\subsection{Academic Year 2023/2024}

\cvitem{}{\textbf{Steven Antya Orvala Waskito}.}
\cvitem{}{\small\textcolor{gray}{OTTER: Sensor Data Processing and Analysis Using Large Language Models (CEG).}}
\cvitem{}{}
\cvitem{}{\textbf{Leong Huen Weng}.}
\cvitem{}{\small\textcolor{gray}{Tracking of Everyday Activities from Voice to Vision Using Large Language Models (CEG).}}
\cvitem{}{}
\cvitem{}{\textbf{Yang Jiacheng}.}
\cvitem{}{\small\textcolor{gray}{Battery-free Sensing and Communication through Tunnel Diodes.}}
\cvitem{}{}
\cvitem{}{\textbf{Goh Jun Yi}.}
\cvitem{}{\small\textcolor{gray}{Networking Mixed Reality Headsets through LiFi.}}
\cvitem{}{}
\cvitem{}{\textbf{Tan Guo Xuan, Marcus}.}
\cvitem{}{\small\textcolor{gray}{Networking Mixed Reality Headsets through LiFi.}}
\cvitem{}{}
\cvitem{}{\textbf{Tang Ethan Yidong}.}
\cvitem{}{\small\textcolor{gray}{Networking Internet of Things through Backhauling Networks.}}
\cvitem{}{}
\cvitem{}{\textbf{Kaemon Ng Chongyu}.}
\cvitem{}{\small\textcolor{gray}{Networking Internet of Things through Backhauling Networks.}}
\cvitem{}{}
\cvitem{}{\textbf{Li Po Hsien}.}
\cvitem{}{\small\textcolor{gray}{Language Models Distributed on Edge Devices.}}

\vspace{0.5em}
\subsection{Academic Year 2022/2023}

\cvitem{}{\textbf{Lim Chang Quan Thaddeus}.}
\cvitem{}{\small\textcolor{gray}{Heartbeat and Breathing Sensing Using Low-Power Wireless Signals (CEG).}}
\cvitem{}{\emph{Led to IEEE RFID 2024 publication.}}
\cvitem{}{}
\cvitem{}{\textbf{Marcus Tang Xin Kye}.}
\cvitem{}{\small\textcolor{gray}{Making Internet of Things Devices Interact with ChatGPT.}}
\cvitem{}{}
\cvitem{}{\textbf{Heng Chen Kai, Darren}.}
\cvitem{}{\small\textcolor{gray}{Sustainable Internet of Things on Capacitors.}}
\cvitem{}{}
\cvitem{}{\textbf{Hu Yuxin}.}
\cvitem{}{\small\textcolor{gray}{Brain Machine Interface.}}
\cvitem{}{}
\cvitem{}{\textbf{Nobel Ang}.}
\cvitem{}{\small\textcolor{gray}{Connecting IoT Devices to Edge and Cloud Devices.}}
\cvitem{}{}
\cvitem{}{\textbf{Wong Chee Hong}.}
\cvitem{}{\small\textcolor{gray}{Computing on Internet of Things Devices.}}
\cvitem{}{}
\cvitem{}{\textbf{Juliet Teoh Qian Ying}.}
\cvitem{}{\small\textcolor{gray}{Computing on Internet of Things Devices.}}

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}
\subsection{Research Assistants and Other Alumni}

\cvitem{}{\textbf{Simon Olofsson}.}
\cvitem{}{Role: Research Assistant.}
\cvitem{}{\small\textcolor{gray}{Convergecast Using Directional Antennas.}}
\cvitem{}{Achievement: Co-authored EWSN 2019 paper.}
\cvitem{}{\emph{Placement: Ph.D.\ at Imperial College London; subsequently at Meta.}}
\cvitem{}{}
\cvitem{}{\textbf{David Hakansson}.}
\cvitem{}{Role: Bachelor Thesis Student.}
\cvitem{}{Thesis: Energy Harvesting Environment Control.}
